The Astropy Project

### 2017-12-07 main.tex
Edits for Section 3.4 to 3.5.5, inclusive

\subsubsection{Barycentric and Heliocentric corrections}
Detailed eclipse or transit
        timing requires accounting for light travel time differences from the
        source to the observatory because of the Earth's motion.
        It is therefore common to instead convert times to the Solar System
        barycenter or heliocenter where the relative timing of photons is
        standardized.
        With the location of a source on the sky (i.e. a \texttt{SkyCoord}
        object), the location of an observatory on Earth (i.e. an
        \texttt{EarthLocation} object), and time values as \texttt{Time}
        objects, the time corrections to shift to the solar system barycenter or
        heliocenter can now be computed with \package{astropy.time} using the
        \texttt{light\_travel\_time} method of a \texttt{Time} object.

@@

The \texttt{NDDataBase} class provides the abstract interface for gridded data
with attributes for accessing metadata, the world-coordinate system (WCS),
uncertainty arrays matched to the data shape, and other traits.
Building on this interface, the \texttt{NDData} class provides a minimal working implementation for storing \package{numpy} arrays. These classes serve as useful base classes for package authors wishing to develop their own classes for specific use cases and as containers for exchanging gridded data.

The classes \texttt{NDDataRef}, \texttt{NDDataArray}, and \texttt{CCDData} extend the base storing functionality with options to do basic arithmetic (addition, subtraction, multiplication, and division) including error propagation in limited cases and slicing of the dataset based on grid coordinates that appropriately handles masking, errors, and units (if present). Additionally, the \texttt{CCDData} class also provides reading and writing from and to FITS files and uses data structures from \astropypkg, like \texttt{WCS}, to represent the contents of a file abstractly.

The \package{astropy.nddata.utils} module provides utilities that can operate on either plain \package{numpy} arrays or any of the classes in the \package{astropy.nddata} subpackage. It features a class for representing two-dimensional image cutouts, allowing one to easily link pixels in the cutout to pixels in the original image or from the image to the cutout, to convert between world and pixel coordinates in the cutout, and to overlay the cutout on images. Functions to enlarge or reduce an image by doing block replication or reduction are also provided.

@@

The \package{astropy.table} subpackage provides functionality for representing
and manipulating heterogeneous data.
%\inlinecomment{APW:}{Need more introduction to the table subpackage!}
The package was described in detail in \cite{astropy}.

Next, we summarize key new features or updates to \package{astropy.table}.

@@

A table can contain data that naturally forms groups -- for example it may
contain multiple observations of a few sources at different points in time
and in different bands. We may then want to split the table into groups based
on the combination of source observed and the band, and then combine the
results for each combination of source and band in some way (for example finding
the mean or standard deviation of the fluxes or magnitudes over time) or filter
the groups based on user-defined criteria. These kinds of grouping and
aggregation operations are now fully supported by \texttt{Table} objects.

@@

\texttt{Table} objects can now be combined in several different ways. If two
tables have the same columns, we may want to stack them ``vertically'' to create a
new table with the same columns but all rows. If two tables are row-matched but
have distinct columns, we may want to stack them ``horizontally'' to create a
new table with the same rows but all columns. For other situations, more general
table concatenations or joins are also possible when two tables share some
common columns.

@@

The \texttt{Table} object now allows \texttt{Quantity} objects, celestial
coordinate objects (\texttt{SkyCoord}), and date/time objects (\texttt{Time}) to
be used as columns, and also provides a general way for other user-defined
objects to be used as columns. This makes it possible for example to easily
represent catalogs of sources or time series as in Astropy, and having both the
benefits of the \texttt{Table} object (such as accessing specific rows/columns
or groups of rows/columns, combining tables, and so on) and the benefits of e.g.
the \texttt{SkyCoord} or \texttt{Time} classes (such as converting the
coordinates to a different frame, or accessing the date/time as a modified
Julian date or in another time scale).

@@

\subsection{Modeling}
\label{sec:modeling}
% The whole modeling submodule was missing from the previous paper, so everything really, including compound models, unit support etc.
% Nadia, Lim
% Tom R. -- unit support
\subsubsection{Overview}
The \package{astropy.modeling} subpackage provides a framework for representing
analytical models and performing model evaluation and parameter fitting. Models and
fitters are independent of each other: a model can be fit with different
fitters and new fitters can be added without changing existing models. The
framework is designed to be flexible and easily extensible. The goal is to have
a rich set of models but also make it easy to create new ones if necessary. The
modeling framework is used in a variety of data analysis tools and is the basis
for the Generalized World Coordinate System (GWCS)
package.\footnote{\url{https://github.com/spacetelescope/gwcs}}

@@

In the next major release after version 3.0, scheduled for the summer of
2018, the focus will be on optimization of the code and improved
documentation.
To prepare for this release, we are preparing software for testing, evaluating,
and monitoring the performance of the code.
Less functionality may be introduced in this release while the focus will be
primarily on improved performance.

>>>>

\subsubsection{Barycentric and Heliocentric corrections}
Detailed eclipse or transit
timing requires accounting for light travel time differences from the
source to the observatory because of the Earth's motion.
It is therefore common to instead convert times to the Solar System
barycenter or heliocenter where the relative timing of photons is
standardized.
With the location of a source on the sky (i.e., a \texttt{SkyCoord}
object), the location of an observatory on Earth (i.e., an
\texttt{EarthLocation} object), and time values as \texttt{Time}
objects, the time corrections to shift to the solar system barycenter or
heliocenter can now be computed with \package{astropy.time} using the
\texttt{light\_travel\_time} method of a \texttt{Time} object.

@@

The \texttt{NDDataBase} class provides the abstract interface for gridded data
with attributes for accessing metadata, the world-coordinate system (WCS),
uncertainty arrays matched to the shape of the data, and other traits.
Building on this interface, the \texttt{NDData} class provides a minimal
working implementation for storing \package{numpy} arrays. These classes serve
as useful base classes for package authors wishing to develop their own classes
for specific use cases and as containers for exchanging gridded data.

The classes \texttt{NDDataRef}, \texttt{NDDataArray}, and \texttt{CCDData}
extend the base storage functionality with options to do basic arithmetic
(addition, subtraction, multiplication, and division), including error
propagation in limited cases, and slicing of the dataset based on grid
coordinates that appropriately handles masking, errors, and units (if present).
Additionally, the \texttt{CCDData} class also provides reading and writing from
and to FITS files and uses data structures from \astropypkg, like \texttt{WCS},
to represent the file contents abstractly.

The \package{astropy.nddata.utils} module provides utilities that can operate
on either plain \package{numpy} arrays or any of the classes in the
\package{astropy.nddata} subpackage. It features a class for representing
two-dimensional image cutouts, allowing one to easily link pixels in the cutout
to those in the original image or vice versa, to convert
between world and pixel coordinates in the cutout, and to overlay the cutout
on images. Functions to enlarge or reduce an image by doing block replication
or reduction are also provided.

@@

The \package{astropy.table} subpackage provides functionality for representing
and manipulating heterogeneous data.
%\inlinecomment{APW:}{Need more introduction to the table subpackage!}
The package was described in detail in \cite{astropy}.
Thus, in what follows, we only summarize key new features or updates to
\package{astropy.table} since the previous \astropy paper.

@@

A table can contain data that naturally form groups; For example, it may
contain multiple observations of a few sources at different points in time
and in different bands. Then, we may want to split the table into groups based
on the combination of source observed and the band, after which we combine the
results for each combination of source and band in some way (e.g., finding
the mean or standard deviation of the fluxes or magnitudes over time) or filter
the groups based on user-defined criteria. These kinds of grouping and
aggregation operations are now fully supported by \texttt{Table} objects.

@@

\texttt{Table} objects can now be combined in several different ways. If two
tables have the same columns, we may want to stack them ``vertically'' to create a
new table with the same columns but all rows. If two tables are row-matched but
have distinct columns, we may want to stack them ``horizontally'' to create a
new table with the same rows but all columns. For other situations, more generic
table concatenation or joining are also possible when two tables share some
columns.

@@

The \texttt{Table} object now allows \texttt{Quantity}, celestial
coordinate (\texttt{SkyCoord}), and date/time (\texttt{Time}) objects to
be used as columns. It also provides a general way for other user-defined
objects to be used as columns. This makes it possible, for instance, to easily
represent catalogs of sources or time series as in \astropy, while having both the
benefits of the \texttt{Table} object (e.g., accessing specific rows/columns
or groups of them and combining tables) and of, for example,
the \texttt{SkyCoord} or the \texttt{Time} classes (e.g., converting the
coordinates to a different frame or accessing the date/time in the desired time scale).

@@

\subsection{Modeling}
\label{sec:modeling}
% The whole modeling submodule was missing from the previous paper, so everything really, including compound models, unit support etc.
% Nadia, Lim
% Tom R. -- unit support

The \package{astropy.modeling} subpackage provides a framework for representing
analytical models and performing model evaluation and parameter fitting. Models and
fitters are independent of each other: a model can be fit with different
fitters and new fitters can be added without changing existing models. The
framework is designed to be flexible and easily extensible. The goal is to have
a rich set of models but also make it easy to create new ones if necessary. The
modeling framework is used in a variety of data analysis tools and is the basis
for the Generalized World Coordinate System (GWCS)
package.\footnote{\url{https://github.com/spacetelescope/gwcs}}

@@

In the next major release after version 3.0, scheduled for
mid-2018, the focus will be on optimization of the code and improved
documentation.
To prepare for this release, we are preparing software for testing, evaluating,
and monitoring the performance of the code.
Less functionality may be introduced in this release while the focus will be
primarily on improved performance.
